Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-20 ms.tex
some clean up of new CO subtraction paragraphs/equations

\subsection{Molecular Emission}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, their broad bandpasses
do not offer the same luxury of spectral resolution in dealing with line 
emission. Thereore, we must subtract estimates of the molecular line 
contamination from each band in order to best isolate the thermal continuum we 
wish to characterize. The most prominent molecular line emission in the
\PLANCK~bands of interest arises from the three lowest CO rotational
transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 GHz and 
J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 217 and 
353 GHz bands.

>>>>

\subsection{Molecular Emission}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, their broad bandpasses
do not offer the same luxury of spectral resolution in dealing with line 
emission. Therefore, we must subtract estimates of the molecular line 
contamination from each \PLANCK~band in order to best isolate the thermal 
continuum we wish to characterize. The most prominent molecular line emission 
in the \PLANCK~bands of interest arises from the three lowest CO rotational
transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 GHz and 
J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 217 and 
353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
\PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
to the dust continuum than J=1$\rightarrow$0 at 100 GHz.

%TODO : actually smooth the CO map to 6.1 arcmin
To correct for molecular emission, we employed the \PLANCK~Type 3 CO 
data product, which boasts the highest S/N 
among the available full-sky CO maps based on \PLANCK~HFI/LFI 
data \citep{planckco}. The native angular resolution of the Type 3 CO map is 
5.5$'$. We therefore began by smoothing the raw Type 3 CO map to $6.1'$, to 
match the PSF of the smoothed \PLANCK~intensity maps we wish to correct 
for molecular emission (for our full-resolution two-parameter fits, these are 
217 GHz and 353 GHz).

%take a few sentences to mention how exactly the CO was scaled, i.e. conversion
% factors from K km/s and line ratio assumptions

We must apply the appropriate unit conversions to the $6.1'$ Type 3 CO
map before we can subtract it from the \PLANCK~intensity maps, which at the
frequencies of interest have native units of $K_{CMB}$. The Type 3 CO map
is provided in units of K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. 
To convert this quantity to $K_{CMB}$, we assume that all of the CO emission 
arises from the $^{12}$CO isotope, and derived the \PLANCK-observed CO 
intensity in units of $K_{CMB}$ as follows:

\begin{equation}
I_{CO, \nu_i, N, N-1} = I_{3}F_{12CO, \nu_i, N, N-1} R_{N, N-1}
\end{equation}

% state what I_3 is 
Where $I_{CO, \nu_i, N, N-1}$ is the intensity in $K_{CMB}$ in \PLANCK~band 
$\nu_i$ due to the CO transition from J=$N$ to J=$(N$$-$1). $I_3$ represents 
the Type 3 CO amplitude in  K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. The 
$F_{12CO, \nu_i, N, N-1}$ are conversion factors between K$_{RJ}$ km/s and 
$K_{CMB}$ for particular band/transition pairs. The relevant values adopted are
$F_{12CO, 100, 1, 0}$=1.478$\times$10$^{-5}$, 
$F_{12CO, 217, 2, 1}$=4.585$\times$$10^{-5}$, and 
$F_{12CO, 353, 3, 2}$=1.751$\times$$10^{-4}$.
$R_{N, N-1}$ represents the line ratio of the transition from J=$N$ to 
J=$(N$$-$1) relative to the J=1$\rightarrow$0. Thus, $R_{1,0}$=1, and we 
further adopt $R_{2,1}$=0.595 and $R_{3,2}$=0.297 based on \cite{planckco}. 
These line ratios are assumed to be constant over the entire sky. Formally, 
then, the CO contamination in band $\nu_i$ is given by:

\begin{equation}
I_{CO, \nu_i} = \sum\limits_{N} I_{CO, \nu_i, N, N-1}
\end{equation}

It turns out that, for each of the \PLANCK~bands in which CO emission is
non-negligible (100, 217 and 353 GHz), only a single $N$ contributes ($N$=1, 
$N$=2 and $N$=3, respectively).

Unfortunately, the CO maps at $6.1'$ are rather noisy,
and the vast majority of the sky has completely negligible CO emission. Thus,
in order to avoid adding unnecessary noise outside of molecular cloud complexes
and at high latitudes, we have zeroed out low-signal regions of the CO Type 3
map. We identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K$_{RJ}$
 km/s, where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ 
resolution. This cut results in 90\% of the sky being unaffected by the CO 
correction, particularly the vast majority of the high Galactic latitude sky.

%did i ever spell out the acronyms HFI, LFI ????
